A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-30 writeup/paper.tex
google translate
google and correlations

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=0.8\linewidth]{final-figures/google-match-bar}
\caption{Translation quality for languages with at least 50 Turkers.  The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We used Google Translate to translate all 10,000 words for each of the 64 foreign language that Google Translate covers. We measured the percent of translations received that exactly matched the translation returned from Google translate. Results are show in Figure \ref{Google-match-bar}. 
Assignments averaged around 43\% overlap with Google translate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

@@

We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.58$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.

>>>>

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=0.8\linewidth]{final-figures/quality-bar}
\caption{Translation quality for languages with at least 50 Turkers.  The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=0.8\linewidth]{final-figures/google-match}
\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
\label{googlematch} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We used Google Translate to translate all 10,000 words for each of the 50 foreign language that Google Translate covers. We measured the percent of translations received that exactly matched the translation returned from Google translate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with Google translate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphaabet) have lower overlap with Google, suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

@@

We ranked the 27 languages based on their translation quality scores according to the external dictionaries, and its calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.53$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.
